The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-22 Writeup/paper_v3.tex
tweaks to conclusions

\rachel{Here is one thing that is still missing from the results
  section.  We had discussed a number of times lumping the galaxies
  together into slices with larger $\Delta z$ and showing that the
  trends in the shape distributions disappear or are reduced.  You had
  shown me plots for this at some point, but they don't seem to have
  gone into the paper.  Please include them, because it would be
  useful to be able to give some guidance on how wide the redshift
  slices should be to avoid this issue.}
\arun{Included now as the last part in the section on results. Do you want me to move it down to this section?}

In this study, we have shown that the shape distributions of galaxies
(to a statistically significant degree) and morphological parameters
like \sersic $n$ and bulge-to-total ratios (more marginally) depend on
the local environments when dividing up the COSMOS sample into
redshift slices along the line of sight.  The redshift slices used had
a width of $\Delta z=0.05$.  Our findings are robust to the choice of
shape estimator from \sersic profile fits vs. using centrally weighted
moments-based shear estimates.

These findings are relevant to attempts to use {\em HST}-based galaxy
samples to calibrate shear estimates in weak lensing surveys.  In
general, the approach would be to define galaxy samples using all
galaxies in redshift slices, and determine a redshift-dependent shear
calibration.  Our findings highlight the danger in such an approach:
while we would like our simulations to include true evolution in
galaxy properties with redshift, this approach also includes spurious
variations in galaxy properties due to the large-scale structure
within the COSMOS field.  Since the fidelity of weak lensing shear
estimates depends sensitively on the intrinsic shape distribution and
galaxy morphological parameters, the conclusions for the
redshift-dependent shear calibration would be incorrect.  These errors
would be reduced as the redshift slices that are used become wider, so
that the impact of local overdensities becomes washed out.

It is important to keep in mind the nature of COSMOS with respect to
other possible {\em HST} training samples.  COSMOS represents the
largest contiguous field surveyed by the {\em HST}, with the sizes of
other {\em HST} fields such as GOODS and AEGIS lagging by at least an
order of magnitude.  Hence, if cosmic variance due to structures along
the line-of-sight in COSMOS are problematic for its use as a training
sample for weak lensing simulations, studies that use even smaller
area training samples are even more prone to errors, with the UDF
serving as an extreme case.  If the size of the {\em HST} survey is
small enough, there is no reason {\em a priori} to suppose that the
galaxy population is typical even when using all galaxies along the
line of sight, without any division into redshift bins.  Of course,
future surveys are unlikely to pick just a single survey to serve as
the basis for their image simulation training sample, but rather
to combine as many as possible.  Combining multiple surveys will
reduce the cosmic variance and therefore the significance of the
effects discussed in this work.  However, with COSMOS being so
dominant in its size, the combination with other much smaller fields
is unlikely to fully ameliorate this effect.  Thus, it will be
important to carefully choose the size of redshift slices used to
derive properties of the galaxy population so as to be minimally
affected by this issue.

>>>>

In this study, we have shown that the shape distributions of galaxies
(to a statistically significant degree) and morphological parameters
like \sersic $n$ and bulge-to-total ratios (more marginally) depend on
the local environments when dividing up the COSMOS sample into
redshift slices along the line of sight.  The redshift slices used for
our primary analysis had
a width of $\Delta z=0.05$.  Our findings are robust to the choice of
shape estimator from \sersic profile fits vs. using centrally weighted
moments-based shear estimates.

These findings are relevant to attempts to use {\em HST}-based galaxy
samples to calibrate shear estimates in weak lensing surveys.  In
general, the approach would be to define galaxy samples using all
galaxies in redshift slices, and determine a redshift-dependent shear
calibration.  Our findings highlight the danger in such an approach:
while we would like our simulations to include true evolution in
galaxy properties with redshift, this approach also includes spurious
variations in galaxy properties due to the large-scale structure
within the COSMOS field.  Since the fidelity of weak lensing shear
estimates depends sensitively on the intrinsic shape distribution and
galaxy morphological parameters, the conclusions for the
redshift-dependent shear calibration would be incorrect.  As shown in
Sec.~\ref{sec:mitigation}, these errors
are reduced as the redshift slices that are used become wider, so
that the impact of local overdensities becomes washed out.  However,
our results suggest that even $\Delta z=0.2$ may not be wide enough
(and this is becoming dangerously close to the size of tomographic
redshift bins to be used for weak lensing analysis in upcoming
surveys).  Thus, more complex schemes may become necessary to fully
overcome this issue.

It is important to keep in mind the nature of COSMOS with respect to
other possible {\em HST} training samples.  COSMOS represents the
largest contiguous field surveyed by the {\em HST}, with the sizes of
other {\em HST} fields such as GOODS and AEGIS lagging by at least an
order of magnitude.  Hence, if cosmic variance due to structures along
the line-of-sight in COSMOS are problematic for its use as a training
sample for weak lensing simulations, studies that use even smaller
area training samples are even more prone to errors, with the UDF
serving as an extreme case.  If the size of the {\em HST} survey is
small enough, there is no reason {\em a priori} to suppose that the
galaxy population is typical even when using all galaxies along the
line of sight, without any division into redshift bins.  Of course,
future surveys are unlikely to pick just a single survey to serve as
the basis for their image simulation training sample, but rather
will combine as many as possible.  Combining multiple surveys will
reduce the cosmic variance and therefore the significance of the
effects discussed in this work.  However, with COSMOS being so
dominant in its size, the combination with other much smaller fields
is unlikely to fully ameliorate this effect.  Thus, it will be
important to carefully choose the size of redshift slices used to
derive properties of the galaxy population so as to be minimally
affected by this issue.
